\documentclass[a4paper, 11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{times}  % Times New Roman font
\setlength{\parskip}{1em}   % paragraph spacing
\hyphenpenalty=10000    % force prevent hyphenation
\linespread{1.5}    % line spacing

% title formatting
\usepackage{titling}
\predate{}  % remove date
\postdate{}
\preauthor{}    % remove author name
\postauthor{}
\title{Statement of Purpose}
\author{}
\date{}

\begin{document}

\maketitle

As the son of a high-school mathematics teacher, it is perhaps not surprising that I grew up to be a deeply analytical person. My desire to study the logic behind everything led me directly to the world of programming. Utilising the free time after my A-Level examinations, I learnt to create static websites and Android applications with the help of great websites like Codecademy and Udemy. Looking back, those projects were laughably simple, but from them a passion for software development was born.


The next step up the ladder was an obvious one, I had to get into an engineering university. Through quite some effort and quite a bit more luck, I managed to obtain a position in the Computer Science and Engineering department of Islamic University of Technology, one of the leading engineering universities in my country. There I became acquainted with faculty members who introduced me to a wide variety of engineering domains, each more interesting than the last, and friends who never failed to provide a competitive learning environment.


Despite the large number of fields I was introduced to, from network engineering to biomedical image processing, in which I ended up doing my undergraduate thesis, my love for software development stuck around. In fact, it grew significantly with the help of the brilliant teachers who taught me everything from basic programming languages and algorithms to more advanced topics like design patterns. With their help, I spent 4 years working on various projects and applications, everyday growing prouder and more confident of my work. This reached its pinnacle when I became the runner-up in a nation-wide game development competition arranged by one of the leading software development companies of my country, BrainStation23. I later went on to do an internship at the same company.


With the end of my undergraduate life in sight, I find myself feeling like I have barely scratched the surface when it comes to the domain of software engineering. I believe I have reached the limits of what can be learnt at my level. This is specifically why I am applying for a position in the Master of Science in Software Engineering program at Technical University of Munich. It is one of the most coveted software engineering programs in the world and will grant me the opportunity to interact with some of the most respected and knowledgeable members of the software engineering community. The fact that the program specifically focuses on the way software is developed at the industry level ensures me that by the end of it, I will be able to make a remarkable entrance into the professional side of the field. My goal is to create software that can be used for social welfare, and I believe that my time in this program will be a significant step towards achieving that goal.


Thank you for taking the time to read this essay. I am looking forward to joining you soon.
\end{document}
